---
title: "Wetland Tables"
author: "Shea Coons"
date: "2/3/2021"
output: html_document
---

```{r setup, include=FALSE}
library(data.table)
library(knitr)
library(reactable)
library(tidyverse)
library(htmlwidgets)
library(webshot)
```

## Ecoregions and colony sites

Below is a plot showing the number of ibis breeding colony sites within each ecoregion. Pair with map of ecoregions?

```{r ecoregion colony table, echo=FALSE}

# Table set up -----
ecoTable <- fread('ecoTable.csv')

# Plot -----
ecoPlot <- ecoTable %>%
  filter(NumColonies < 150) %>% 
  arrange(NumColonies) %>%    # First sort by val. This sort the dataframe but NOT the factor levels
  mutate(Ecoregion=factor(Ecoregion, levels=Ecoregion)) %>%   # This trick update the factor levels
  ggplot( aes(x=Ecoregion, y= NumColonies)) +
  # geom_segment( aes(xend=Ecoregion, yend=0)) +
  geom_point( size=10, color="orange") +
  coord_flip() +
  geom_text(aes(label=NumColonies), vjust= 0.4, color = 'white', size=3.5) +
  xlab('Ecoregion') +
  ylab("Number of Breeding Colonies") +
  ggtitle("Breeding Colonies by Region") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))

```

## West-wide WFIB Habitat

Below is a table showing overall wetland information for the ecoregions included in the study. 
All values are in hectares.

```{r overall wetland table, echo = FALSE}

# Table set up -----

hydro05 <- fread('summaryTable_wetlands.csv')
hydro06<- hydro05 %>%
  mutate_if(is.numeric, ~round(.,0))

# Table ----
reactable(hydro06, striped = T)
```

## WetType Table

Below is a table showing the wetland types (function groups) used in the study, their descriptions, and total area in hectares (note: not the total area of water, total area overall!).

```{r wetType, echo=FALSE}

# Read in Table -----

wetType <- fread('wetType_table.csv')

# Table -----
reactable(wetType, striped = T)

```

## Raw Data Sample Table

Below is a table showing a sample of the water surface area data used in the study.

```{r sample data, echo=FALSE}

# Read in Table -----

sampleDat <- fread('rawDataSample_table.csv')

# Table -----
reactable(sampleDat, striped = T)

```


## RF Variables Summary Table 

Below is a table showing a summary of the climate and irrigation variables used in the random forest analysis. 

```{r RF vars, echo=FALSE}

# read in table -----
summary <- fread('RFvarsSummary.csv')

# Reduce number of numbers after decimal

summary01 <- summary %>% 
  mutate_if(is.numeric, ~round(.,0))

# Rename columns -----

colnames(summary01) <- c('Variable', 'Region', '1983-2003 (T1)', 'SD (T1)', '2004-2020 (T2)', 'SD (T2)', 'Change', '% Dif', 'Num. Wilcox-p Sig.', 'Num. LM-p Sig.')

# Format table -----
  # Will need to subset by variable -----

    aet <- summary01 %>% 
      filter(Variable == 'aet')
  
    pr <- summary01 %>% 
      filter(Variable == 'pr')
    
    swe <- summary01 %>% 
      filter(Variable == 'swe')
    
    ro <- summary01 %>% 
      filter(Variable == 'ro')
    
    tmin <- summary01 %>% 
      filter(Variable == 'tmin')
    
    irr <- summary01 %>% 
      filter(Variable == 'irr_ha')
    
  # Make Tables -----
    # aet -----
      reactable(
        aet,
        pagination = FALSE,
        fullWidth = F,
        columns = list(
          Variable = colDef(
            style = JS("function(rowInfo, colInfo, state) {
              var firstSorted = state.sorted[0]
              // Merge cells if unsorted or sorting by school
              if (!firstSorted || firstSorted.id === 'Variable') {
                var prevRow = state.pageRows[rowInfo.viewIndex - 1]
                if (prevRow && rowInfo.row['Variable'] === prevRow['Variable']) {
                  return { visibility: 'hidden' }
                }
              }
            }")
          )
        ),
        outlined = TRUE
      )
    # pr -----
      reactable(
        pr,
        pagination = FALSE,
        fullWidth = F,
        columns = list(
          Variable = colDef(
            style = JS("function(rowInfo, colInfo, state) {
              var firstSorted = state.sorted[0]
              // Merge cells if unsorted or sorting by school
              if (!firstSorted || firstSorted.id === 'Variable') {
                var prevRow = state.pageRows[rowInfo.viewIndex - 1]
                if (prevRow && rowInfo.row['Variable'] === prevRow['Variable']) {
                  return { visibility: 'hidden' }
                }
              }
            }")
          )
        ),
        outlined = TRUE
      )
    
    # swe -----
      reactable(
        swe,
        pagination = FALSE,
        fullWidth = F,
        columns = list(
          Variable = colDef(
            style = JS("function(rowInfo, colInfo, state) {
              var firstSorted = state.sorted[0]
              // Merge cells if unsorted or sorting by school
              if (!firstSorted || firstSorted.id === 'Variable') {
                var prevRow = state.pageRows[rowInfo.viewIndex - 1]
                if (prevRow && rowInfo.row['Variable'] === prevRow['Variable']) {
                  return { visibility: 'hidden' }
                }
              }
            }")
          )
        ),
        outlined = TRUE
      )
    
    # ro -----
      reactable(
        ro,
        pagination = FALSE,
        fullWidth = F,
        columns = list(
          Variable = colDef(
            style = JS("function(rowInfo, colInfo, state) {
              var firstSorted = state.sorted[0]
              // Merge cells if unsorted or sorting by school
              if (!firstSorted || firstSorted.id === 'Variable') {
                var prevRow = state.pageRows[rowInfo.viewIndex - 1]
                if (prevRow && rowInfo.row['Variable'] === prevRow['Variable']) {
                  return { visibility: 'hidden' }
                }
              }
            }")
          )
        ),
        outlined = TRUE
      )
    
    # tmin -----
      reactable(
        tmin,
        pagination = FALSE,
        fullWidth = F,
        columns = list(
          Variable = colDef(
            style = JS("function(rowInfo, colInfo, state) {
              var firstSorted = state.sorted[0]
              // Merge cells if unsorted or sorting by school
              if (!firstSorted || firstSorted.id === 'Variable') {
                var prevRow = state.pageRows[rowInfo.viewIndex - 1]
                if (prevRow && rowInfo.row['Variable'] === prevRow['Variable']) {
                  return { visibility: 'hidden' }
                }
              }
            }")
          )
        ),
        outlined = TRUE
      )
    
    # irr -----
      reactable(
        irr,
        pagination = FALSE,
        fullWidth = F,
        columns = list(
          Variable = colDef(
            style = JS("function(rowInfo, colInfo, state) {
              var firstSorted = state.sorted[0]
              // Merge cells if unsorted or sorting by school
              if (!firstSorted || firstSorted.id === 'Variable') {
                var prevRow = state.pageRows[rowInfo.viewIndex - 1]
                if (prevRow && rowInfo.row['Variable'] === prevRow['Variable']) {
                  return { visibility: 'hidden' }
                }
              }
            }")
          )
        ),
        outlined = TRUE
      )

# Save table (optional) -----
table <- reactable(
  summary01,
  pagination = FALSE,
  columns = list(
    Variable = colDef(
      style = JS("function(rowInfo, colInfo, state) {
        var firstSorted = state.sorted[0]
        // Merge cells if unsorted or sorting by school
        if (!firstSorted || firstSorted.id === 'Variable') {
          var prevRow = state.pageRows[rowInfo.viewIndex - 1]
          if (prevRow && rowInfo.row['Variable'] === prevRow['Variable']) {
            return { visibility: 'hidden' }
          }
        }
      }")
    )
  ),
  outlined = TRUE
)

html <- 'table.html'
saveWidget(table, html)
webshot(html, 'tableSnapshot.png')

```


## Proportions Table 

Below is a table showing a summary of the mean overlap between land ownership, hydroperiod, and wetland type.

```{r Proportions Table, echo=FALSE}

# read in tables -----
gb <- fread('proGB.csv')
mr <- fread('proMR.csv')
md <- fread('proMD.csv')
np <- fread('proNP.csv')
nr <- fread('proNR.csv')
pnw <- fread('proPNW.csv')
sp <- fread('proSP.csv')
sr <- fread('proSR.csv')

gb01 <- gb
colnames(gb01) <- c('Region', 'Hydroperiod', 'Ownership', 'WetType', 'WetArea')

# Make Tables -----
  # GB -----
    reactable(
      gb,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
        Region = colDef(
          width = 250,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )

  # MR -----
    reactable(
      mr,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
        Region = colDef(
          width = 250,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )
  
  # MD -----
    reactable(
      md,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
         Region = colDef(
          width = 250,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )
  
  # NP -----
    reactable(
      np,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
         Region = colDef(
          width = 250,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )

  # NR -----
      reactable(
        nr,
        pagination = FALSE,
        fullWidth = T,
        columns = list(
          Region = colDef(
          width = 250,
            style = JS("function(rowInfo, colInfo, state) {
              var firstSorted = state.sorted[0]
              // Merge cells if unsorted or sorting by school
              if (!firstSorted || firstSorted.id === 'Region') {
                var prevRow = state.pageRows[rowInfo.viewIndex - 1]
                if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                  return { visibility: 'hidden' }
                }
              }
            }")
          )
        ),
        outlined = TRUE
      )
  
  # PNW -----
    reactable(
      pnw,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
         Region = colDef(
          width = 250,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )

  # SP -----
    reactable(
      sp,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
         Region = colDef(
          width = 250,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )
  
  # SR -----
    reactable(
      sr,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
         Region = colDef(
          width = 250,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )
```

## Class Summary Tables by Region 

Below are tables showing summaries of wetland change across wetland type, ownership and hydroperiod.

```{r Class Table, echo=FALSE}

# read in tables -----
gb <- fread('table_gb_types.csv')
mr <- fread('table_mr_types.csv')
md <- fread('table_md_types.csv')
np <- fread('table_np_types.csv')
nr <- fread('table_nr_types.csv')
pnw <- fread('table_pnw_types.csv')
sp <- fread('table_sp_types.csv')
sr <- fread('table_sr_types.csv')

# Make Tables -----
  # GB -----
    reactable(
      gb,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
        perDif = colDef(width = 80),
        Region = colDef(
          width = 220,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )

    # MR -----
    reactable(
      mr,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
        perDif = colDef(width = 80),
        Region = colDef(
          width = 220,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )
  
  # MD -----
    reactable(
      md,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
        perDif = colDef(width = 80),
         Region = colDef(
          width = 220,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )
  
  # NP -----
    reactable(
      np,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
        perDif = colDef(width = 80),
         Region = colDef(
          width = 220,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )

  # NR -----
      reactable(
        nr,
        pagination = FALSE,
        fullWidth = T,
        columns = list(
          perDif = colDef(width = 80),
          Region = colDef(
          width = 220,
            style = JS("function(rowInfo, colInfo, state) {
              var firstSorted = state.sorted[0]
              // Merge cells if unsorted or sorting by school
              if (!firstSorted || firstSorted.id === 'Region') {
                var prevRow = state.pageRows[rowInfo.viewIndex - 1]
                if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                  return { visibility: 'hidden' }
                }
              }
            }")
          )
        ),
        outlined = TRUE
      )
  
  # PNW -----
    reactable(
      pnw,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
        perDif = colDef(width = 80),
         Region = colDef(
          width = 220,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )

  # SP -----
    reactable(
      sp,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
        perDif = colDef(width = 80),
         Region = colDef(
          width = 220,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )
  
  # SR -----
    reactable(
      sr,
      pagination = FALSE,
      fullWidth = T,
      columns = list(
        perDif = colDef(width = 80),
         Region = colDef(
          width = 220,
          style = JS("function(rowInfo, colInfo, state) {
            var firstSorted = state.sorted[0]
            // Merge cells if unsorted or sorting by school
            if (!firstSorted || firstSorted.id === 'Region') {
              var prevRow = state.pageRows[rowInfo.viewIndex - 1]
              if (prevRow && rowInfo.row['Region'] === prevRow['Region']) {
                return { visibility: 'hidden' }
              }
            }
          }")
        )
      ),
      outlined = TRUE
    )

```